Nested sampling with two objective functions

### 2016-01-07 Paper/ms.tex
contributions
removed instructions

\section{Failure modes}

@@

BJB initiated the project and explored various ideas which did not work.

Required if more than one author. Authorship must include and be strictly limited to researchers who have substantially contributed to the reported work. Please carefully review our criteria regarding the Qualification for Authorship: \web /instructions.

>>>>

\section{Failure modes}\label{sec:failure_modes}

@@

BJB initiated the project and explored various ideas which did not work.
EC worked on the biased sampling suggestion in Section~\ref{sec:rationale},
discovered the failure mode in Section~\ref{sec:failure_modes}, ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
